\phantomsection
\addcontentsline{toc}{section}{Preface}
%
{\parskip 1ex
\section*{Preface}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%{\huge {\bf Preface}}\\[5mm]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section*{Preface}
                                                                     
                                             
Welcome to \mlss, Sydney, 2015. This time we find ourselves in Sydney, Australia and what a gorgeous spot this is.

Machine Learning is a foundational discipline that forms the basis of much modern statistical data analysis. As data science emerges to meet the challenges of Big Data, understanding the theory and practice of machine learning becomes a crucial asset in academia and industry.
The machine learning summer school provides graduate students, academics and industry professionals with an intense learning experience on the theory and applications of modern machine learning. 

This time \mlss runs over ten days, including two technical sessions (approximately 2.5h each) per day during Monday 16th February to Wednesday 25th February, except for Saturday and Sunday, which will be free days. There will also be six practical tutorial sessions (approximately 1.5h each) aimed at clarifying/reinforcing concepts through practice. The school will have a strong focus on probabilistic inference,  Bayesian non-parametrics and applications to recommender systems, computer vision and document analysis. 

The program is pretty tight and we will be having 20min coffee breaks for each technical session and 1h lunches each day.  Last but not least, as not everything in life is work and networking is a crucial part of academic and professional life, we will get together for dinner and drinks on Tuesday 24th February, all while  cruising the  beautiful surroundings of  Sydney Harbour.

A huge thanks to the speakers for providing such an invaluable academic service. We are also very grateful to our lab assistants for designing the practical sessions. 

That is enough from us. Now go and enjoy \mlss  and tell us what you think. It's great to see you.






\bigskip

Edwin V.~Bonilla, Fabio Ramos and Yang Wang.

% \begin{tabular}{p{3in}p{3in}}
% Hugh Durrant-Whyte & Cyrill Stachniss\\
% Nicholas Roy & Pieter Abbeel \\
% Gaurav Sukhatme  & Danica Kragic \\
% Stefan Schaal
% \end{tabular}

}
